\documentclass{article}
\usepackage{amsmath}
\usepackage{array}

\newcommand\todo[1]{\textcolor{blue}{[TODO: #1]}}
\newcommand\TODO[1]{\textcolor{blue}{\small [TODO: #1]}}

\newenvironment{eqdesc}
  {\par\vspace{\abovedisplayskip}\noindent\begin{tabular}{>{$}l<{$} @{${}\hspace{0.6cm}{}$} l}}
  {\end{tabular}\par\vspace{\belowdisplayskip}}

\include{definitions}

\begin{document}

\section{Symbols used in ``Metro Maps on Octilinear Grid Graphs''}

%\author{Patrick Brosi\\\affaddr{University of Freiburg}\\\affaddr{Chair of Algorithms and Data Structures}}

\subsection{General}

\begin{eqdesc}
	\iG = (\iV, \iE)     &  Input graph with nodes $\iv \in \iV$ and edges $\ie = (u, v) \in \iE$ \\
	\drawing{\iG} = (\drawingpossym, \drawingcurvesym)     &  Drawing of $\iG$, $\drawingpos{\iv}$ assigns a position to every $\iv \in \iV$, $\drawingcurve{e}$ \\
	 & assigns a curve to every $\ie \in \iE$. \\   
	\initdrawing{\iG} &  The initial embedding of $\iG$. \\
	L^{\infty} & Uniform norm. \\
	\gScale & scale factor of our grid, essentially the grid cell dimension \\
	\gmind & min distance between edges in octilinear drawing
\end{eqdesc}

\subsection{Grid Graph}

\begin{eqdesc}
	\gG  = (\gV, \gE)     &  Octilinear grid graph with nodes $\gv \in \gV$ and edges $\ge \in \gE$.\\
	\ggv{x}{y} & Original grid node at position $(x, y)$. \\
	\gpv{x}{y}{p}  & $p$-th port node of grid node $\ggv{x}{y}$. \\
	\gse{x}{y}{p}  & $p$-th sink edge for node $\ggv{x}{y}$. \\
	\gbe{x}{y}{p}{\phi}  & Bend edge for angle $\phi$ at port $p$ for grid node at $x, y$. \\
	\gPath      	 & Path on octilinear grid graph. \\
	\gPathOcti      & Path on updated octilinear grid graph with bend edges. \\
	\gPturn{\phi}  & Turn penalty for angle $\phi$. \\
	\gPturnEdge{\phi}  & Actual turn penalty cost used in octilinear grid graph. \\
	\gHopcost    & Hop cost in grid graph (cost of a single edge in the original grid graph) \\
	\gHopcostOcti &   Actual hop cost in the octilinear grid graph. \\
	\gSinkcost & Sink cost in grid graph. \\
	\gPcost{\gPath}  & Path cost on original grid graph. \\
	\gPcostOcti{\gPathOcti}  & Path cost on octilinear grid graph.

\end{eqdesc}

\subsection{Integer Linear Program}

\begin{eqdesc}

\gvused{\gv}{\iv} & bin. decision variable whether grid node $\gv$ is assigned to input node $\iv$.\\
\geused{\ge}{\ie} & bin. decision variable whether grid edge $\ge$ is used be input edge $\ie$.\\
\dir{\iv}{\ie} & variable telling the direction of edge $\ie$ at node $\iv$.\\
\dirdiff{\ie}{f}	& variable telling the direction difference of edge $\ie$ and edge $f$.\\
\bend{\ie}{f}{\phi} & bin. decision  variable telling whether the direction difference of edge $\ie$ and\\
                    & edge $f$ is $i \times 45^{\circ}$.

\end{eqdesc}

\end{document}
